---
title: "COVID study factor structure "
output: html_notebook
---

# Write and examine in data 

From the plots below we can see there is a large missing data problem. For the sake of simplicity I have retained participants who completed > 50% of the study
```{r}
survey <- read_rds("reduced_international_student_survey.rds") %>% 
  tibble::rowid_to_column(var = "p_id")

survey %>% 
  visdat::vis_miss()

survey %>% 
  visdat::vis_dat()

survey_adequate_sample <- survey %>% 
  filter(prop_miss_all < .5) #delete cases with < 50% missing data 


covid_labels <- survey_adequate_sample %>% 
  select(contains("covid")) %>% 
  labelled::look_for() %>% 
  tidyr::separate(
    col = label, 
    into = c("instruction", "question"),
    sep = ". - "
  ) %>% 
  select(-instruction) %>% 
  remove_rownames() %>% 
  column_to_rownames("variable")
```

# Covid Questions

The COIVD questions are n ot pre-validated. I am going look at factor solutions for these questions to create a composite score/s

## Plotting responses 
```{r}

survey_adequate_sample %>% 
  select(
    contains("covid")
  ) %>% 
psych::describe() %>% 
  select(-mad, 
         -min,
         -trimmed,
         -max, 
         -range, 
         -kurtosis) %>% 
  mutate_all(round, 2) %>% 
knitr::kable(format = 'html',
             caption =  "COIVD variables") %>% 
  kableExtra::kable_styling()


survey_adequate_sample %>% 
  select(
    p_id,
    contains("covid")
  ) %>% 
  mutate_all(as.numeric) %>% 
  pivot_longer(
    -p_id,
    names_to = "Question", 
    values_to = "Response"
  ) %>% 
  drop_na(Response) %>% 
  mutate(Question = as_factor(Question)) %>% 
  ggplot(
    aes(x = Response,
        color = Question,
        fill = Question
        )
  ) + 
  facet_wrap(facets = ~ Question) + 
  geom_histogram(bins =5)+
  ggtitle("Hisotgram of Reponses to COVID Questions") +
  theme_classic()
  
```

## Exploratory factor analysis COVID questions

I have undertaken 3 EFA (1, 2, and 3 factor models).
```{r}
covid_vars <- survey_adequate_sample %>% 
  select(covid_19_stress_1:covid_19_stress_13) %>% 
  as.matrix()


psych::scree(covid_vars)

psych::fa.parallel(
  covid_vars,
  fa = "fa"
)
  

covid_fa_2 <- psych::fa(
  covid_vars, 
  nfactors = 2
)

covid_fa_1 <- psych::fa(
  covid_vars, 
  nfactors = 1
)

covid_fa_3 <- psych::fa(
  covid_vars, 
  nfactors = 3
)

covid_fa_4 <- psych::fa(
  covid_vars, 
  nfactors = 4
)

```

```{r}
fa.lookup(
  covid_fa_1, 
  dictionary = covid_labels
  ) %>% 
  data.frame() %>% 
  rownames_to_column(var = "Question ID") %>% 
  select(
    "Question ID", 
    "question",
    everything()
  ) %>% 
  knitr::kable(format = 'html',
               caption = "1 factor") %>% 
  kableExtra::kable_styling()

psych::fa.diagram(covid_fa_1)
```

```{r}
fa.lookup(
  covid_fa_2, 
  dictionary = covid_labels
)  %>% 
  rownames_to_column(var = "Question ID") %>% 
  select(
    "Question ID", 
    "question",
    everything()
  ) %>% 
  knitr::kable(format = 'html',
               caption = "2 factors") %>% 
  kableExtra::kable_styling()

psych::fa.diagram(covid_fa_2)
```

```{r}
fa.lookup(
  covid_fa_3, 
  dictionary = covid_labels
) %>% 
  rownames_to_column(var = "Question ID") %>% 
  select(
    "Question ID", 
    "question",
    everything()
  ) %>% 
  knitr::kable(format = 'html', 
               caption = "3 factors") %>% 
  kableExtra::kable_styling()

psych::fa.diagram(covid_fa_3)

```

```{r}
fa.lookup(
  covid_fa_4, 
  dictionary = covid_labels
) %>% 
  rownames_to_column(var = "Question ID") %>% 
  select(
    "Question ID", 
    "question",
    everything()
  ) %>% 
  knitr::kable(format = 'html', 
               caption = "3 factors") %>% 
  kableExtra::kable_styling()

psych::fa.diagram(covid_fa_4)

```