---
title: "analyse_surveys"
author: "Joel larwood"
date: "2020-07-02"
output:
  html_document:
    df_print: paged
    toc: no
  html_notebook: default
  workflowr::wflow_html:
    code_folding: hide
    toc: no
editor_options:
  chunk_output_type: console
---

```{r housekeep}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      error = FALSE)
```

```{r pacakges, echo = FALSE, message=FALSE}
library(tidyverse)
library(ggpubr)
library(naniar)
library(kableExtra)
library(apa)
```

```{r loadin}

survey_analysis_data <- read_rds(
  here::here(
    "data",
    "adequately_sampled.rds"
  )
)

```

## Introduction {.tabset}

In this section I provide the results of statistical analyses relating to the survey questions. 

### Working Situation

```{r}

chi_sq_dat <- survey_analysis_data %>% 
  mutate(at_home = if_else(current_circumstance == "Staying at home for study/work",
                           TRUE,
                           FALSE)) %>%
  select(at_home, student_status)

```

Due to covid a number of different working situations were present. I am particulary interested in the proportions who were working from home rather than leaving the home. International students were more likely to be working from home than domestic students, `r apa::chisq_apa(stats::chisq.test(table(chi_sq_dat)), format = "rmarkdown")`

```{r}
broom::tidy(table(chi_sq_dat)) %>% 
  knitr::kable(format = "html") %>% 
  kableExtra::kable_styling()

means <- survey_analysis_data %>% 
  select(student_status,
         covid_stress:psycheck) %>% 
  group_by(student_status) %>% 
  summarise_if(is.numeric, 
               list(mean, sd), na.rm = TRUE)

wellbeing_t <- apa::t_apa(t.test(formula = wellbeing ~ student_status, data = survey_analysis_data, var.equal = TRUE), format = "rmarkdown")

psycheck_t <- apa::t_apa(t.test(formula = psycheck ~ student_status, data = survey_analysis_data, var.equal = TRUE), format = "rmarkdown")

covid_emotions <- apa::t_apa(t.test(formula = emotional_response ~ student_status, data = survey_analysis_data, var.equal = TRUE), format = "rmarkdown")

covid_stress_t <- apa::t_apa(t.test(formula = covid_stress ~ student_status, data = survey_analysis_data, var.equal = TRUE), format = "rmarkdown")
```

### Wellbeing Surveys

International students (M = `r round(as.numeric(means[2, 4]), 2)`, SD = `r round(as.numeric(means[2, 8]),2)`) and domestic students M = `r round(as.numeric(means[1, 4]),2)`, SD = `r round(as.numeric(means[1, 8]),2)`) had equitable wellbeing, as measured by the Warick Edinburgh, *t*(387) = -0.91, *p* = .364, *d* = -0.09.  

International students (M = `r round(as.numeric(means[2, 5]),2)`, SD = `r round(as.numeric(means[2, 9]),2)`) and domestic students M = `r round(as.numeric(means[1, 5]),2)`, SD = `r round(as.numeric(means[1, 9]),2)`) had also had equitable scores on the PsyCheck *t*(386) = -0.96, *p* = .337, *d* = -0.10. 

There was also no difference between international students (M = `r round(as.numeric(means[2, 3]),2)`, SD = `r round(as.numeric(means[2, 7]),2)`) and domestic students M = `r round(as.numeric(means[1, 3]),2)`, SD = `r round(as.numeric(means[1, 7]),2)`), *t*(399) = -0.88, *p* = .378, *d* = -0.09. 

However, international students had higher COVID stress (M = `r round(as.numeric(means[2, 2]),2)`, SD = `r round(as.numeric(means[2, 6]),2)`) than domestic students (M = `r round(as.numeric(means[1, 2]),2)`, SD = `r round(as.numeric(means[1, 6]),2)`), *t*(399) = -4.28, *p* < .001, *d* = -0.43.


## Correlations between Music use and surveys {.tabset}

### Music and COVID stress 

```{r}
music_covid <- lm(
  as.numeric(music) ~ as.numeric(covid_stress),
  data = survey_analysis_data
)

music_covid_status <- lm(
  as.numeric(music) ~ as.numeric(covid_stress) * as.factor(student_status),
  data = survey_analysis_data
)

sjPlot::tab_model(music_covid,
                  music_covid_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

interactions::interact_plot(music_covid_status,
                            pred = covid_stress,
                            modx = student_status) +
  ggplot2::ylim(1,6) +
  theme_classic()
```

### Emotional response and Music
```{r}
music_covid_emotion <- lm(
  as.numeric(music) ~ as.numeric(emotional_response),
  data = survey_analysis_data
)

music_covid_emotion_status <- lm(
  as.numeric(music) ~ as.numeric(emotional_response) * as.factor(student_status),
  data = survey_analysis_data
)

sjPlot::tab_model(music_covid_emotion,
                  music_covid_emotion_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

interactions::interact_plot(music_covid_emotion_status,
                            pred = emotional_response,
                            modx = student_status) +
  ggplot2::ylim(1,6) +
  theme_classic()
```


### Wellbeing and Music
```{r}
music_wellbeing <- lm(
  as.numeric(music) ~ as.numeric(wellbeing),
  data = survey_analysis_data
)

music_wellbeing_status <- lm(
  as.numeric(music) ~ as.numeric(wellbeing) * as.factor(student_status),
  data = survey_analysis_data
)

sjPlot::tab_model(music_wellbeing,
                  music_wellbeing_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

interactions::interact_plot(music_wellbeing_status,
                            pred = wellbeing,
                            modx = student_status) +
  ggplot2::ylim(1,6) +
  theme_classic()
```

### PsyCheck and Music
```{r}
music_psycheck <- lm(
  as.numeric(music) ~ as.numeric(psycheck),
  data = survey_analysis_data
)

music_psycheck_status <- lm(
  as.numeric(music) ~ as.numeric(psycheck) * as.factor(student_status),
  data = survey_analysis_data
)

sjPlot::tab_model(music_psycheck,
                  music_psycheck_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

interactions::interact_plot(music_psycheck_status,
                            pred = psycheck,
                            modx = student_status) +
  ggplot2::ylim(1,6) +
  theme_classic()
```