---
title: "Music Analyses"
author: "Joel larwood"
date: "2020-07-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r}
library(lubridate)
library(tidyverse)
```

## Introduction

```{r}
spotify <- read_rds("data/spotify_added.rds") 

lyrics <- read_rds(
  here::here(
    "data",
    "spotify_lyrics.Rds"
  )
)

stop_words <- tidytext::stop_words

lyrics_tidy <- lyrics %>% 
  tidytext::unnest_tokens(
    word, lyric
  ) %>% 
  anti_join(stop_words)%>% 
  inner_join(tidytext::get_sentiments("afinn")) %>% 
  group_by(id) %>% 
  summarise(sentiment = mean(value)) 



spotify_added <- full_join(
  spotify,
  lyrics_tidy,
  by = "id"
)


```

## Relationships with scales and music {.tabset}

### Valence

#### Correlation between valence and covid stress

```{r}
music_valence_covid <- lm(
  as.numeric(valence) ~ as.numeric(covid_stress),
  data = spotify_added
)

music_valence_covid_status <- lm(
  as.numeric(valence) ~ as.numeric(covid_stress) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_valence_covid,
                  music_valence_covid_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))
```

#### Correlation between valence and emotional response 

```{r}
music_valence_covid_emotion <- lm(
  as.numeric(valence) ~ as.numeric(emotional_response),
  data = spotify_added
)

music_valence_covid_emotion_status <- lm(
  as.numeric(valence) ~ as.numeric(emotional_response) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_valence_covid_emotion,
                  music_valence_covid_emotion_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

#### Correlation between valence and wellbeing
```{r}
music_valence_wellbeing <- lm(
  as.numeric(valence) ~ as.numeric(wellbeing),
  data = spotify_added
)

music_valence_wellbeing_status <- lm(
  as.numeric(valence) ~ as.numeric(wellbeing) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_valence_wellbeing,
                  music_valence_wellbeing_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

#### PsyCheck and Valence
```{r}
music_valence_psycheck <- lm(
  as.numeric(valence) ~ as.numeric(psycheck),
  data = spotify_added
)

music_valence_psycheck_status <- lm(
  as.numeric(valence) ~ as.numeric(psycheck) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_valence_psycheck,
                  music_valence_psycheck_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

### Lyrical Sentiment 

#### Correlation between sentiment and covid stress

```{r}
music_sentiment_covid <- lm(
  as.numeric(sentiment) ~ as.numeric(covid_stress),
  data = spotify_added
)

music_sentiment_covid_status <- lm(
  as.numeric(sentiment) ~ as.numeric(covid_stress) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_sentiment_covid,
                  music_sentiment_covid_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))
```

#### Correlation between sentiment and emotional response 

```{r}
music_sentiment_covid_emotion <- lm(
  as.numeric(sentiment) ~ as.numeric(emotional_response),
  data = spotify_added
)

music_sentiment_covid_emotion_status <- lm(
  as.numeric(sentiment) ~ as.numeric(emotional_response) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_sentiment_covid_emotion,
                  music_sentiment_covid_emotion_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

#### Correlation between sentiment and wellbeing
```{r}
music_sentiment_wellbeing <- lm(
  as.numeric(sentiment) ~ as.numeric(wellbeing),
  data = spotify_added
)

music_sentiment_wellbeing_status <- lm(
  as.numeric(sentiment) ~ as.numeric(wellbeing) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_sentiment_wellbeing,
                  music_sentiment_wellbeing_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

#### PsyCheck and sentiment
```{r}
music_sentiment_psycheck <- lm(
  as.numeric(sentiment) ~ as.numeric(psycheck),
  data = spotify_added
)

music_sentiment_psycheck_status <- lm(
  as.numeric(sentiment) ~ as.numeric(psycheck) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_sentiment_psycheck,
                  music_sentiment_psycheck_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```


### Energy

#### Correlation between energy and covid stress

```{r}
music_energy_covid <- lm(
  as.numeric(energy) ~ as.numeric(covid_stress),
  data = spotify_added
)

music_energy_covid_status <- lm(
  as.numeric(energy) ~ as.numeric(covid_stress) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_energy_covid,
                  music_energy_covid_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))
```

#### Correlation between energy and emotional response 

```{r}
music_energy_covid_emotion <- lm(
  as.numeric(energy) ~ as.numeric(emotional_response),
  data = spotify_added
)

music_energy_covid_emotion_status <- lm(
  as.numeric(energy) ~ as.numeric(emotional_response) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_energy_covid_emotion,
                  music_energy_covid_emotion_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

#### Correlation between energy and wellbeing
```{r}
music_energy_wellbeing <- lm(
  as.numeric(energy) ~ as.numeric(wellbeing),
  data = spotify_added
)

music_energy_wellbeing_status <- lm(
  as.numeric(energy) ~ as.numeric(wellbeing) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_energy_wellbeing,
                  music_energy_wellbeing_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

#### PsyCheck and energy
```{r}
music_energy_psycheck <- lm(
  as.numeric(energy) ~ as.numeric(psycheck),
  data = spotify_added
)

music_energy_psycheck_status <- lm(
  as.numeric(energy) ~ as.numeric(psycheck) * as.factor(student_status),
  data = spotify_added
)

sjPlot::tab_model(music_energy_psycheck,
                  music_energy_psycheck_status,
                  show.aic = TRUE,
                  show.std = TRUE,
                  dv.labels = c("Music", "Music"))

```

